Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2023-11-21 LaTeX_paper/paper.tex
add result pictures
start fixing margins
Add more test cases

% to set the margin of the page
\usepackage[a4paper, total={6.5in, 9in}]{geometry}

@@

\subsection{Setup}
The test sample consist in 5 different puzzles:
\begin{itemize}
  \item a 4x4 real world puzzle
  \item a 8x8 real world puzzle
  \item a 4x4 digital puzzle
  \item a 8x8 digital puzzle
  \item a 16x16 digital puzzle
\end{itemize}
The real world puzzles have been obtained with a printer’s scanner,
and the digital puzzles have been obtained from \url{https://puzzle.telegnom.org/}.

@@

\subsection{Results}

\begin{table}[H]
  \centering
  \begin{tabular}{
  >{\columncolor[HTML]{D9EAD3}}c 
  >{\columncolor[HTML]{D0E0E3}}c 
  >{\columncolor[HTML]{E6B8AF}}c 
  >{\columncolor[HTML]{FCE5CD}}c }
  \cellcolor[HTML]{B6D7A8} &
    \cellcolor[HTML]{A2C4C9} &
    \multicolumn{2}{c}{\cellcolor[HTML]{EA9999}Execution time {[}s{]}} \\
  \multirow{-2}{*}{\cellcolor[HTML]{B6D7A8}Size} &
    \multirow{-2}{*}{\cellcolor[HTML]{A2C4C9}Pieces} &
    \cellcolor[HTML]{DD7E6B}Digital puzzle &
    \cellcolor[HTML]{F9CB9C}Real Puzzle \\
  4x4   & 16  & 4   & 59   \\
  8x8   & 64  & 30  & 2851 \\
  16x16 & 256 & 377 & N/A 
  \end{tabular}
\end{table}

\subsection{Accuracy}
It is crucial to mention that the project currently lacks an automated
method for evaluating the accuracy of results. However, the accuracy
of the two real-world puzzles has been manually confirmed,
with both achieving a 100\% correctness.

@@

>>>>

% to set the margin of the page
\usepackage[a4paper, left=25mm,top=20mm,bottom=20mm,right=15mm]{geomet ry}

@@

\subsection{Setup}
We have tested many different sizes of real, and digital puzzles.
The real world puzzles have been obtained with a printer’s scanner, more data are available in REF SETUP.
The digital puzzles have been obtained from \url{https://puzzle.telegnom.org/}.
This web app can generate a puzzle from a dimension and a jitter value. The jitter is a parameter that controls
how unique and distorted the puzzle images are, see \ref{fig:jiiter}.
The default jitter used in the tests is 5\%.

\begin{figure}[H]
  \caption{Effect of jitter on jigsaw pieces}\label{fig:jiiter}
  \centering
  \includegraphics[height=0.3\textwidth]{pictures/jitter.png}
\end{figure}

@@

\subsection{Digital vs Real World Puzzles}

In the table below we can see how the same algorithm
can have vastly different performance depending on the kind of puzzle 
it is working with.
\begin{table}[H]
  \centering
  \begin{tabular}{
  >{\columncolor[HTML]{D9EAD3}}c 
  >{\columncolor[HTML]{D0E0E3}}c 
  >{\columncolor[HTML]{F4CCCC}}c 
  >{\columncolor[HTML]{FCE5CD}}c }
  \cellcolor[HTML]{B6D7A8} &
    \cellcolor[HTML]{A2C4C9} &
    \multicolumn{2}{c}{\cellcolor[HTML]{EA9999}Execution time {[}s{]}} \\
  \multirow{-2}{*}{\cellcolor[HTML]{B6D7A8}Size} &
    \multirow{-2}{*}{\cellcolor[HTML]{A2C4C9}Pieces} &
    \cellcolor[HTML]{DD7E6B}Digital puzzle &
    \cellcolor[HTML]{F9CB9C}Real Puzzle \\
  2x3   & 6   & 1   & 4    \\
  3x4   & 12  & 3   & 14   \\
  4x4   & 16  & 4   & 59   \\
  4x5   & 20  & 4   & 48   \\
  5x8   & 40  & 20  & 627  \\
  8x8   & 64  & 30  & 2851 \\
  8x12  & 96  & 660 & N/A  \\
  16x16 & 256 & 377 & N/A 
  \end{tabular}
\end{table}

Looking at the data we can spot to anomalies:
\begin{itemize}
  \item The 4x5 real puzzle has a lower execution time than the 4x4 real puzzle. This is not a big
  difference and can be attribute to run to run variation.
  \item The 8x12 digital puzzle has a much higher execution time than the 16x16 digital puzzle.
  This is also easily explainable, as puzzles whose side is not a power of two are in general
  harder compared to those who fulfill this condition. As they require an extra step compared to
  the simple algorithm shown in section REF.
\end{itemize}

\subsubitem{Effect of Jitter on Execution Time}

Intuitively increasing the jitter would make the pieces harder to
match with each other, and consequently making the puzzle easier to solve.
And we can observe that this intuition is correct in the table below.

\begin{table}[H]
  \centering
  \begin{tabular}{
  >{\columncolor[HTML]{D0E0E3}}c 
  >{\columncolor[HTML]{C9DAF8}}c }
  \multicolumn{2}{c}{\cellcolor[HTML]{B6D7A8}Jitter effect on an 8x8 digital puzzle} \\
  \cellcolor[HTML]{A2C4C9}Jitter   & \cellcolor[HTML]{A4C2F4}Execution time {[}s{]}  \\
  4\%                              & 104                                             \\
  5\%                              & 30                                              \\
  6\%                              & 17                                              \\
  8\%                              & 17                                              \\
  10\%                             & 16                                             
  \end{tabular}
  \end{table}

This shows how the execution time can be six times faster just by making
each piece more unique. This notion can be applied to the real world puzzle,
in fact the current version of the comparator REF is not using the color
of the piece, only the shape. Adding the color to the available
data could significantly increase the uniqueness of each piece,
bringing down the execution time.

\subsection{Run to Run Variation}

Another feature of the algorithm that is worth testing is his consistency.
The table below shows how the algorithm performs using a set of different
same-sized puzzles as input.
\begin{table}[H]
  \centering
  \begin{tabular}{
  >{\columncolor[HTML]{FCE5CD}}c 
  >{\columncolor[HTML]{FFF2CC}}c 
  >{\columncolor[HTML]{EAD1DC}}c }
  \multicolumn{3}{c}{\cellcolor[HTML]{EA9999}Run to run vairance on a 4x4 real puzzle}                                                             \\
  \cellcolor[HTML]{F9CB9C}Execution time {[}s{]} & \cellcolor[HTML]{FFE599}Avrege                 & \cellcolor[HTML]{D5A6BD}Standard deviation     \\
  64 & \cellcolor[HTML]{FFF2CC} & \cellcolor[HTML]{EAD1DC} \\
  68 & \cellcolor[HTML]{FFF2CC} & \cellcolor[HTML]{EAD1DC} \\
  43 & \cellcolor[HTML]{FFF2CC} & \cellcolor[HTML]{EAD1DC} \\
  24 & \cellcolor[HTML]{FFF2CC} & \cellcolor[HTML]{EAD1DC} \\
  29 & \cellcolor[HTML]{FFF2CC} & \cellcolor[HTML]{EAD1DC} \\
  59 & \multirow{-6}{*}{\cellcolor[HTML]{FFF2CC}47.8} & \multirow{-6}{*}{\cellcolor[HTML]{EAD1DC}18.6}
\end{tabular}
\end{table}

\subsection{Accuracy}
It is crucial to mention that the project currently lacks an automated
method for evaluating the accuracy of results. However, the accuracy
of two real-world puzzles (4x4 and 8x8) has been manually confirmed,
with both achieving a 100\% correctness.

@@

\begin{figure}[h]
  \caption{example of a result render of a digital puzzle}\label{fig:result_digital}
  \centering
  \includegraphics[height=0.6\textwidth]{pictures/result_digital.png}
\end{figure}

\begin{figure}[h]
  \caption{example of a result render of a real world puzzle}\label{fig:result_real}
  \centering
  \includegraphics[height=0.6\textwidth]{pictures/result_real.png}
\end{figure}
